---
title: "R_ShortIntro"
author: "Sejin Park"
date: "2014년 10월 7일"
output: ioslides_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


## Slide with R Code and Output

```{r}
getwd()
setwd("~/Documents/Dropbox/biopythonstudy/part2/part2ch13")
```

## Slide with R Code and Output

```{r}
10^2 + 36
a <- 4 ; a
a*5
a = a+10; a
```

## Data structures

- vector 
- matrix
- dataframe
- list

## Vectors

```{r}
vec1 = c(1,4,6,8,10) ; vec1
vec1[5] 
vec1[3]
vec1[3]=12 ; vec1
```
## Vectors

```{r}
vec2 = 1:10
vec2[1]
vec2[-1]
sum(vec2)
```

## Matrices
```{r}
mat = matrix(data = c(9,2,3,4,5,6), ncol=3); mat
mat[1,2]; mat[2,]
mean(mat)
```

## Dataframes
```{r}
t = data.frame(x=c(11,12,14), y=c(19,20,21), z = c(10,9,7));  t
mean(t$z)
mean(t[["z"]])
```

## Lists
```{r}
L = list(one=1, two = c(1,2), five = seq(0,1,length=5)); L
names(L);  L$five + 10
```

## Graphics
```{r}
plot(rnorm(100), type="l", col="gold")
```

## Graphics - histogram
```{r}
hist(rnorm(100))
```


## Reading and writing data files

```{r}
d = data.frame(a= c(3,4,5), b = c(12,43,54))
d
write.table(d, file="tst0.txt", row.names=FALSE)
d2 = read.table(file="tst0.txt", header=TRUE)
d2
```

## not available data

```{r}
j = c(1,2,NA)
max(j)
max(j, na.rm=TRUE)
```

## Classes - Characters
```{r}
m = "apples"
m
```

## If-statements
```{r}
w=3
if(w<5)
  {
  d=2
  }else{
  d=10  
  }
d
```

## For-loop
```{r}
h = seq(from=1, to=8)
s = c()
for(i in 2:10)
  {
  s[i] = h[i] * 10
  }
s
```
## writing your own functions
```{r}
fun1 = function(arg1, arg2)
  {
  w = arg1 ^2
  return(arg2 + w)
  }
fun1(arg1 = 3, arg2 = 5)

```

## install packages

- CRAN 
- devtools : github
- bioconductor (http://www.bioconductor.org)
- > source("http://bioconductor.org/biocLite.R")
- > biocLite("affy")

## CRAN
- install.packages("ggplot2")

## devtools
- install.packages("devtools")
- Windows: Install Rtools.
- Mac: Install Xcode from the Mac App Store.
- Linux: Install a compiler and various development libraries 

## devtools
- Mac and Linux:
- devtools::install_github("hadley/devtools")

- Windows:
- library(devtools)
- build_github_devtools()

## example : rCharts
- http://ramnathv.github.io/rCharts/
- require(devtools)
- install_github('rCharts', 'ramnathv')

## bioconductor
- bioconductor (http://www.bioconductor.org)
- source("http://bioconductor.org/biocLite.R")
- biocLite("affy")




## ggplot2

```{r}
# ggplot2 examples
library(ggplot2) 

# create factors with value labels 
mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5),
     labels=c("3gears","4gears","5gears")) 
mtcars$am <- factor(mtcars$am,levels=c(0,1),
     labels=c("Automatic","Manual")) 
mtcars$cyl <- factor(mtcars$cyl,levels=c(4,6,8),
   labels=c("4cyl","6cyl","8cyl")) 
```

## ggplot2

```{r}
# Kernel density plots for mpg
qplot(mpg, data=mtcars, geom="density", fill=gear, alpha=I(.5), 
   main="Distribution of Gas Milage", xlab="Miles Per Gallon", 
   ylab="Density")
```

## ggplot2
```{r}
p <- qplot(hp, mpg, data=mtcars, shape=am, color=am, 
   facets=gear~cyl, main="Scatterplots of MPG vs. Horsepower",
   xlab="Horsepower", ylab="Miles per Gallon")
p + theme_bw()
p + theme(axis.title=element_text(face="bold.italic", 
   size="12", color="brown"), legend.position="top")

```

## reference
- http://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf
- A (very) short introduction to R 
- Paul Torfs & Claudia Brauer
